---
title: "Homework Week 8"
author:
- UTRGV School of Mathematical and Statistical Sciences.
- STAT 4332 Experimental Design
- Norb Lara
output:  html_notebook
---

---

>**Objective:** One-Way ANOVA: Practical problems

---


### Problems:

* An experimenter has conducted a single-factor experiment with four levels of the factor, and each factor level has been replicated six times.  The computed value of the F-statistic is $F_0 = 3.26.$  Find the P-value.

\begin{aligned}
factor levels:    k &= 4 \\
replicates:       n &= 6*k = 6(4) = 24 \\
degrees of freedom:    df1 &= k-1 = 4-1 = 3 \\
df2 &= n-k = 24-4 = 20 \\
\\
p-value &= 0.0430\\
\end{aligned}

```{r, echo=TRUE}
pf(3.26,3,20,lower.tail = FALSE)
```
---
---
* An experiment has conducted a single-factor completely randomized design with three levels of factors and five replicates. The computed value of the F-statistic is $F_0=2.91.$ Find the P-value.

\begin{aligned}
factor levels:    k &= 3 \\
replicates:       n &= 5*k = 5(3) = 15 \\
degrees of freedom:    df1 &= k-1 = 3-1 = 2 \\
df2 &= n-k = 15-3 = 12 \\
\\
p-value &= 0.09325\\
\end{aligned}
```{r}
pf(2.91,2,12,lower.tail = FALSE)
```
---
---
* The tensile strength of Portland cement is being studied.  Four different mixing techniques can be used economically.  A completely randomized experiment was conducted and the following data were
collected that represents Tensile Strength (lb/in$^2$).

    Mixing Technique |     |      |      |      |
    ---              | --- | ---  | ---  | ---  | 
    1                |3129 | 3000 | 2865 | 2890 |
    2                |3200 | 3300 | 2975 | 3150 |
    3                |2800 | 2900 | 2985 | 3050 |   
    4                |2600 | 2700 | 2600 | 2765 |    
    * **Make a scatter or a box-plot that help you visualize distribution's attributes such as variance 
    and mean.**
```{r}
# Data for tensile strengths
tensile_strength <- data.frame(
  Technique = factor(rep(1:4, each = 4)),
  Strength = c(3129, 3000, 2865, 2890,
               3200, 3300, 2975, 3150,
               2800, 2900, 2985, 3050,
               2600, 2700, 2600, 2765)
)

# Create a boxplot
boxplot(Strength ~ Technique, data = tensile_strength,
        xlab = "Mixing Technique",
        ylab = "Tensile Strength (lb/in^2)",
        main = "Boxplot of Tensile Strength by Mixing Technique",
        col = rainbow(4)
)
```

    * **Test the hypothesis that mixing techniques affect the strength of the cement.  Use $\alpha= 
    0.05.$**\
    As shown below, since our P-value is very small. We reject our null hypothesis\

    * **Use the Fisher LSD method with $\alpha= 0.05$ to make comparisons between pairs of means.** \
    The groups are significantly different except for group 1 and 3 which crosses the zero

    * **Construct a normal probability plot of the residuals.  What conclusion would you draw about the
    validity of the normality assumption?** \
    The data follows closely to the normally distributed line. Therefore or normality assumption is correct.\

    * **Plot the residuals versus the predicted tensile strength.  Comment on the plot.** \
    Residuals do not have increased variability which shows assumption of equal variance is correct \

    * **Use Tukey’s test with $\alpha = 0.05.$  Do you get the same conclusions from Tukey’s test that 
    you did with the Fisher LSD method?** \
    No \

    
  ---
  ---
    
* **Reconsider previous experiment.  Find a 95 percent confidence interval on the mean tensile strength of the Portland cement produced by each of the four mixing techniques.  Also find a 95 percent confidence interval on the difference in means for techniques 1 and 3.  Does this aid in interpreting the results of the experiment?** \


---
---
* A pharmaceutical manufacturer wants to investigate the bioactivity of a new drug.  A completely randomized single-factor experiment was conducted with three dosage levels, and the following results were obtained.

  Dosage  |     |      |      |      |
    ---   | --- | ---  | ---  | ---  | 
    20g   |24 | 28 | 37 | 30 |
    30g   |37 | 44 | 31 | 35 |
    40g   |42 | 47 | 52 | 38 |   
    * **Is there evidence to indicate that dosage level affects bioactivity?  Use $\alpha = 0.05.$** \
    With a small P-value, there is evidence to indicate that bioactivity is different. We reject the null\

    * **If it is appropriate to do so, make comparisons between the pairs of means.  What conclusions can
    you draw?** \
    the 40g and 20g have significantly different means\

    * **Analyze the residuals from this experiment and comment on the model adequacy.** \
    Residuals do not have increased variability which shows assumption of equal variance is correct \

---
---
* Problem to be solved with R: Consider the dataset  ToothGrowth `data(ToothGrowth)` wheres the response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day). Perform ANOVA analysis to show whether the dose of vitamin C has an effect in tooth grow. Support your analysis with graphics and perform a means comparison analysis using the `TukeyHSD` function (read documentation for such function). Hint: you may need need to use `as.factor(dose)` for both `aov` function and Tukeys.    
    
    

