---
title: "Homework Week 1"
author:
- UTRGV School of Mathematical and Statistical Sciences
- STAT 4332 Experimental Design
- Norb Lara 
- SID 0173147
output:  html_notebook
---

---
>**Objective:** Use the R notebook to present homework reports in a standard and organized manner.


* Consider the following paired data $(x,y)$:

| --- | --- | --- | --- | --- | --- | --- | ---  | ---  | ---  | --- |  <br>
$x$ | 1   | 2   | 3   | 4   | 5   | 6   | 7    | 8    | 9    | 10       <br>
$y$ | 2.20| 4.06| 4.33| 5.95| 6.02| 8.65| 10.70| 11.56| 10.71| 12.07    <br>
  * Use the function `lm` to conduct a linear regression and display the results with function     `summary`. <br>
  * Compute the *total sum of squares* SST and the *error sum of squares* SSE and compute the **coefficient of determination $R^2$** as $1-\frac{SSE}{SST}.$ There are many ways to do this. For example you can use the function `residuals` or you can store your model `mod <- lm()` and use the access `mod$fitted.values` and `mod$residuals`. 
  


Using the Simple Linear Regression Model:
$$ Y = \beta_0 + \beta_1X + \epsilon$$
---
<!-- {r} - indicates R code
      ` is an "accent grave" (ave as in have) also called back tick
      ` is under the tilde-->
```{r}
x <- c(1:10)
y <- c(2.20, 4.06, 4.33, 5.95, 6.02, 8.65, 10.70, 11.56, 10.71, 12.07)
z <- x + y
print(z)
```



Our Linear Model Summary is
```{r}
Linear_model.lm <- lm(formula = y ~ x)
summary(Linear_model.lm)
```



The plot of the Regression Line is
```{r}
plot(x = x, y = y, xlab = "x values", ylab = "y values", main = "Homework 1")
```



 Computing the coefficient of determination:
 $$ R^2 = \frac{SSR}{SST} = \frac{\sum_{i=1}^{n}(\hat y_i - \bar y)^2}{\sum_{y_i - \bar y)^2}} = 1 - \frac{SSE}{SST}$$
 
 
```{r}
# summary(Linear_model.lm)$r.squared
# SSE = sum(Linear_model.lm$residuals**2)

SST = sum((y - mean(y))**2)
SSR = sum((Linear_model.lm$fitted.values - mean(y))**2)
SSE = sum((Linear_model.lm$fitted.values - y)**2)

(SST - SSE) / SST

SSR / SST

1 - SSE / SST
```
 
 
 